---
title: "Assignment_shiny_app"
author: "Wojciech Starosta"
date: "9.10.2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Reproducible Pitch Presentation

This is an presentation for Reproducible Pitch Assignment. It will introduce how parametrization of decision tree influence obtained results. We will focus on airquality data using two packages:

```{r packages, echo = TRUE}
library(shiny)
library(rpart)
library(rpart.plot)
```

Shiny app:
(https://wojciechstarosta.shinyapps.io/Developing-data-products-shiny-app/)

Source Code:
(https://github.com/wojciechstarosta/Developing-data-products-shiny-app)


## Data summary

```{r airquality, echo = TRUE}
summary(airquality)
```

## Interactive elements

In this tool You can check how parametrization of elements below influence final tree structure:

- minimal value of observation in a leaf (used to check if tree can divide further),
- maximum depth of a tree (used to set how deep tree should grow),
- number of cross-validations (used to obtain cross-validation error for overfitting issue),
- estimation method (you can choose between Anova and Poisson).

## Predictive methodology: CART

Estimation method used in this exercise is CART (package rpart). Standard output is as follows:

```{r tree, echo = TRUE}
tree1<-rpart(formula=Ozone ~ .,airquality, method="anova", cp=0,
             maxdepth=5,minbucket=10, xval=10)
prp(tree1, box.palette = "Reds", tweak = 1.2)
```